Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-07 implementation.tex
updated implementation section for AE

\subsection{HZ}
We have developed a simple reference implementation, HZ, of Hazelnut.  In
order to reach a wide audience, we decided to implement HZ in the web
browser.  In order to take advantage of a mature implementation of the FRP
model, we chose to implement HZ using
OCaml\footnote{\url{https://ocaml.org/}}, the \texttt{js\_of\_ocaml}
compiler and associated libraries
\cite{DBLP:conf/ml/Balat06}\footnote{\url{http://ocsigen.org/js\_of\_ocaml/}}
and the OCaml React
library\footnote{\url{http://erratique.ch/software/react}}.

At the time of the writing, HZ's view computation renders the model as a
string embedded into HTML that approximates our typeset notation in this
paper. The action palette is a collection of buttons and text boxes, which
are disabled when an action is not well-defined or an invalid action
argument is entered. We determine this by simply attempting to perform the
action internally and catching the exception that is raised when an action
is undefined. This design, of course, is not meant to score marks for
usability or performance. Instead, as a simple reference implementation, we
expect its source code to be of use to others who are interested in
layering a more fluid user interface atop the core semantics (which have
been implemented in a style that follows the presentation in this paper
closely), or extensions thereof.

>>>>

\subsection{HZ}
We have developed a simple reference implementation, HZ, of Hazelnut extended with sum types as described in Sec. \ref{sec:extending}.  In
order to reach a wide audience, we decided to implement HZ in the web
browser.  In order to take advantage of a mature implementation of the FRP
model, we chose to implement HZ using
OCaml\footnote{\url{https://ocaml.org/}}, the \texttt{js\_of\_ocaml}
compiler and associated libraries
\cite{DBLP:conf/ml/Balat06}\footnote{\url{http://ocsigen.org/js\_of\_ocaml/}}
and the OCaml React
library\footnote{\url{http://erratique.ch/software/react}}.

The core semantics have
been implemented in a functional style that follows the presentation in this paper closely.

The view computation renders the model (i.e. a Z-expression paired with a type) as nested HTML \texttt{div} elements matching the tree structure of the corresponding Z-expression. This tree is stylized separately using CSS. The action palette is a collection of buttons and text boxes which
are disabled when the corresponding action cannot be performed. We determine this by simply attempting to perform the
action internally and handling the exception that is raised when an action
is undefined. Each action form also has a corresponding keyboard shortcut. This design is not, of course, meant to score marks for
usability or performance. Instead, as a simple reference implementation, we
expect its source code to be of use to others who are interested in
layering a more fluid user interface atop the core semantics, or extensions thereof.
